\begin{rSection}{Research Experience}
\begin{rSubsection}{Electro-Adhesive Crawling Robot}{2023 - Now}{Undergraduate Reserach Program Research Topic}{BioRobotics LAB, SRRC}
  \item Using HASEL Actuator integrated with Electro Adhesive Module to make the climbing robot.
  \item Key Words: Electro-Adhesive, HASEL Actuator, Climbing Robot
\end{rSubsection}

\begin{rSubsection}{Multi Objects Gripper System Development}{2022 - Now}{Research Topic}{BioRobotics LAB, SRRC}
  \item Develop the underactuated soft gripper of 3 fingers with 1 motor driven and design its control sytem to simulating in the Isaac Sim. Then create optimized strategy to grasp multi-objects.
  \item Key Words: Underactuated, Tendon Driven, Multi-Object Grasping, Isaac Sim
\end{rSubsection}

\begin{rSubsection}{Robot Control System Development}{2021 - 2022}{Research Assistant}{State Key Laboratory of Synthetical Automation for Process Industries}
  \item Learned the communication between Low-level servo drivers and host computer in Ethercat and CAN.
  \item Self defined and tested ros controllers in `ros control' framework.
\end{rSubsection}

\begin{rSubsection}{Dual-Mode Teleoperation with Variable Admittance Control}{2020-2021}{Undergraduate Student Research Assistant}{NEU Human Robot Collaborate Lab}
  \item Designed and developed an innovative teleoperating framework with 2 IMU sensors and a robotic arm manipulator.
  \item Researched control algorithms for a robotic arm manipulator with variable admittance control.
\end{rSubsection}

\begin{rSubsection}{Multi-mode Control Technologies of Exoskeleton Robot}{Undergraduate Thesis}{Undergraduate Student Research Assistant}{NEU Human Robot Collaborate Lab}
  \item Developed robot hardware interface module with ROS2 Framework in real-time control.
  \item Designed and developed the compliant control algorithm on this robot to enhance the human machine collaboration ability.
  \item GitHub: \href{https://github.com/MingshanHe/NEU_Exoskeleton}{NEU-Exoskeleton}.
\end{rSubsection}

% \begin{rSubsection}{Hybrid Robot for Following and Grasping project}{Course Design}{Group Leader}{Faculty of Robot Science and Engineering}
%   \item Designed and developed a control system for hybrid robot (6-DoF Robotic Arm and Mobile Platform) to follow the target and grasp it.
% \end{rSubsection}

\end{rSection}

